Modeling Intervention Strategies for United States TB Control

### 2013-10-14 in_progress/presentations/paper/draft.tex
wording change

The majority of USB and FB individuals fall into the Susceptible (S) category, which includes everyone
who is uninfected and has not been exposed to TB.  After exposure to an individual
with TB, a person in the Susceptible compartment can develop Latent TB Infection (LTBI) and changes
health states to either the Acute LTBI (F) or Chronic LTBI (L) compartment.  Latently
infected individuals are not infectious, but have some risk of developing active TB infection
over time.  However, the rates of disease progression are not equal, and individuals in the
Acute LTBI compartment have a higher risk of developing active TB than those in
the Chronic LTBI compartment.  Individuals in the Chronic LTBI compartment
may also be exogenously re-infected and transition to the Acute LTBI compartment.  \\

@@

CtBase = Ct,
ClBase = Cl
)
    \end{verbatim}
  }
  \end{center}
  \caption{A list of relevant constants in the Basic \& Extended Hill Model}
  \label{fig:basicHillConstants}
\end{figure}<++>
\subsection{The Extended Hill Equations}
Below, we detail the full equations used in the extended hill model. These
equations extend those used in the standard Hill Model. In many cases, the
equations of the Hill model were split into their component parts, which could
then be tracked separately. 
\begin{figure}[h]
  \begin{center}
  \tiny{
    \begin{verbatim}
discV   <- 1/(1.03^t)  #amount costs, health states discount constant

>>>>

The majority of USB and FB individuals fall into the Susceptible (S) category,
which includes everyone who is uninfected and has not been exposed to TB.  After
exposure to an individual with TB, a person in the Susceptible compartment can
develop Latent TB Infection (LTBI). Latently infected individuals are
asymptomatic and non-infectious, but have some risk of developing active TB
infection over time. In order to reflect the fact that real LTBI patients have a
much higher risk of developing active TB within two years of exposure, the Hill
Model splits the LTBI compartment into Acute LTBI (fast progressors) and Chronic
LTBI (slow progressors). Accordingly, individuals in the Acute LTBI compartment
have a higher risk of developing active TB than those in the Chronic LTBI
compartment.  Individuals in the Chronic LTBI compartment may also be
exogenously re-infected and transition to the Acute LTBI compartment.  \\

@@

CtBase = Ct,
ClBase = Cl
)
    \end{verbatim}
  }
  \end{center}
  \caption{A list of relevant constants in the Basic \& Extended Hill Model}
  \label{fig:basicHillConstants}
\end{figure}
\subsection{The Extended Hill Equations}
Below, we detail the full equations used in the extended hill model. These
equations extend those used in the standard Hill Model. In many cases, the
equations of the Hill model were split into their component parts, which could
then be tracked separately. 
\begin{figure}[h]
  \begin{center}
  \tiny{
    \begin{verbatim}
discV   <- 1/(1.03^t)  #amount costs, health states discount constant
